---
title: "Script for newData"
author: "Rebecca Goulancourt"
output: pdf_document
---

```{r}
path_output <- "/Users/rgoulanc/Desktop/Rebecca/FAC/M1BI-IPFB/SEM2/Stage/BERRET_BOSTOEN/R/NewData/Outputs"
path_inputs <- "/Users/rgoulanc/Desktop/Rebecca/FAC/M1BI-IPFB/SEM2/Stage/BERRET_BOSTOEN/R/NewData/Inputs"
library(stringr)
```


Period = function() {
  library(stringr)
  f <- unlist(str_extract_all(alldata[i], "\\d+"))[2]
  f <- as.numeric(f)*10^-3   # mHz -> Hz
  period <- 2/(f)
  cat("The period of one oscillation is : ", period, "\n")
  
  start_osc <- 10
  end_osc <- 15
  psirad_value <- NULL
  nrow <- 0
  for (i in 1:nrow(data)) {
    if (start_osc <= data$time.s[i] & data$time.s[i] <= end_osc) {
      nrow <-  nrow + 1
      psirad_value[i] <- data$psi.t..rad[i]
    } 
  } 
  psirad_value <- na.omit(psirad_value)
  psimaxR <- max(psirad_value)
  cat("number of value of psi(t) (on 1 oscillation) : ", nrow, "\n",
      "maximum of the oscillation : ", psimaxR)
  
  plot(data$time.s, data$psi.t..rad, main = "angular frequency vs time (1 oscillation)",
       sub = alldata[i],
       xlab = "time (s)",
       ylab = "angular frequency (rad)",
       type = "l",
       xlim = c(10, 10 + period),
       ylim = c(-3,0))
  
}


  max <- NULL
  for (i in 2:nrow(data)) {
    if (i == nrow(data)) {
      break
    }
    if (data$psi.t..rad[i] > data$psi.t..rad[i-1] & data$psi.t..rad[i] > data$psi.t..rad[i+1]) {
      max <- rbind(max, as.data.frame(data[i, 1:2]))
      
    }
  }
  max <- na.omit(max)
  
  #outliers (false peak of the curve)
  diff_max <- diff(max$psi.t..rad)
  mean_diff_max <- mean(diff_max)
  box <- boxplot(diff_max)
  cat("outliers : ", box$out)
  
  diff_max_int <- diff_max[!diff_max %in% box$out]
  mean_diff_max_int <- mean(diff_max_int)
  box2 <- boxplot(diff_max_int)
  
```{r}
Maximum_curve = function(file) {
  max <- NULL
  for (i in 2:nrow(data)) {
    if (i == nrow(data)-1) {
      break
    }
    if (data$psi.t..rad[i] > data$psi.t..rad[i-1] & data$psi.t..rad[i] > data$psi.t..rad[i+1]) {
      max <- rbind(max, as.data.frame(data[i, 1:2]))
      
    }
  }
  max <- na.omit(max)
  
  #outliers (false peak of the curve)
  diff_max <- diff(max$psi.t..rad)
  mean_diff_max <- mean(diff_max)
  box <- boxplot(diff_max)
  cat("outliers : ", box$out, rep("\n", 2))
  plot(diff_max)
  lines(diff_max)
  
  #outlier_ligne <- NULL
  #for (i in 1:length(diff_max)) {
  #outlier_ligne[i] <- which(box$out[i] == diff_max)
  #}
  #outlier_ligne <- na.omit(outlier_ligne)
  #which(box$out == diff_max)
  
  diff_max_int <- diff_max[!diff_max %in% box$out]
  #colnames(diff_max_int)[1] <- "diff_max_int"
  mean_diff_max_int <- mean(diff_max_int)
  box2 <- boxplot(diff_max_int)
  
  setwd(path_output)
  write.table(diff_max_int, file = paste(file, "max_curve.txt", sep = "_"), append = FALSE, sep = "\t", col.names = TRUE)
  
}
```

```{r}
Maximum_point = function(file) {
  
max <- NULL
for (i in 2:nrow(data)) {
  if (data$psi.t..rad[i] > data$psi.t..rad[i-1] & data$psi.t..rad[i] > data$psi.t..rad[i+1]) {
    max <- rbind(max, as.data.frame(data[i, 1:2]))
    if (nrow(max) == 2) { break }
  }
}
max <- na.omit(max)
#hyp_point <- nrow(data)/nrow(max) # number of points for 1 oscillation
numb_point <- as.numeric(rownames(max))
numb_point <- sum(numb_point)/2 # nb de points moyens pour 1 oscillation


max_osc <- NULL
vec <- NULL
k <- 1
for (i in 1:nrow(data)) {
  if (i == nrow(data)) { break }
  if (i <= k + numb_point) {
    vec[i] <- data$psi.t..rad[i]
  }
  else if (i >= k + numb_point) {
    k <- k + numb_point
    vec <- na.omit(vec)
    max_osc[i] <- max(vec)
    vec <- NULL
  }
}
max_osc <- na.omit(max_osc)
max_osc <- as.data.frame(max_osc)

setwd(path_output)
write.table(max_osc, file = paste(file, "max_osc.txt", sep = "_"), append = FALSE, sep = "\t", col.names = TRUE)

}
```

```{r}
Maximum_drop = function(file) {
  
max_drop <- NULL
for (i in 2:nrow(data)) {
  if (i >= nrow(data)) { break }
  if (data$psi.t..rad[i+1] <= data$psi.t..rad[i] - data$psi.t..rad[i]*4/100) {
    max_drop[i] <- data$psi.t..rad[i-1]
    #eval.parent(substitute(i <- i+5))
    i %+=% 3
    print(i)
  }
  if (i > 30) { break }
}

max_drop <- na.omit(max_drop)
max_drop <- as.data.frame(max_drop)

setwd(path_output)
write.table(max_drop, file = paste(file, "max_drop.txt", sep = "_"), append = FALSE, sep = "\t", col.names = TRUE)

}
```


```{r}
Maximum_chg = function(file) {
  chg <- NULL # changements relatifs
  for (i in 1:nrow(data)) {
    if (i == nrow(data)) { break }
    chg[i] <- (data$psi.t..rad[i+1]-data$psi.t..rad[i])/data$psi.t..rad[i]
  }
  plot(chg, ylim = c(-0.2, 0.05), xlim = c(500, 600))
  lines(chg)
  abline(h = 0, col = "blue") # on prends i-2
  #si dessus alors courbe monte
  #drop = drop de valeur dans la courbe donc un max juste avant
  chg0 <- which(chg == 0)
  chg_pos <- which(chg > 0)
  chg_neg <- which(chg < 0)
  
  diff_mean <- mean(diff(chg))
  x <- diff_mean - 4/100
  abline(h = x, col = " green")
  
  max_chg <- NULL
  for (i in 2:length(chg)) {
    if (i == length(chg)) { 
      break
    }
    if (chg[i] < chg[i-1] & chg[i] < 0 & chg[i+1] <= chg[i] + (chg[i]*5/100)) {
      if (i > 2) {
        max_chg[i] <- data$psi.t..rad[i-2]
      }
    }
  }
  max_chg <- as.data.frame(na.omit(max_chg))
  colnames(max_chg)[1] <-  "max"
  
  time <- NULL
  for (i in 1:nrow(max_chg)) {
    for (j in 1:nrow(data)) {
      if (max_chg$max[i] == data$psi.t..rad[j]) {
        time[i] <-data$time.s[j]
      }
      #if (i == nrow(max_chg)) { break }
    }
  }
  time <- as.data.frame(time)
  max_dat <- cbind(time, max_chg)
  
  setwd(path_output)
  write.table(max_dat, file = paste(file, "max_chg.txt", sep = "_"), append = FALSE, sep = "\t", col.names = TRUE)
}
```

  

```{r}
data <- NULL
alldata <- list.files(path = path_inputs, ".txt", full.names = FALSE)
for (i in 1:length(alldata)) {
  setwd(path_inputs)
  data <- read.table(alldata[i], header = TRUE, sep = "\t", dec = ".")

  par(mfrow=c(1,1))
  plot(data$time.s, data$psi.t..rad, main = "angular frequency vs time", sub = alldata[i],
       xlab = "time (s)",
       ylab = "angular frequency (rad)",
       type = "l")
  plot(data$time.s, data$psi.t..rad, main = "angular frequency vs time", sub = alldata[i],
       xlab = "time (s)",
       ylab = "angular frequency (rad)",
       type = "p",
       xlim = c(155, 180))
  lines(data$time.s, data$psi.t..rad, col = "red")
  #dev.print(device = pdf, file = "Rplot2.pdf", width = 300)

  if (alldata[i] == "alldata_film10_104mHz.txt") {
  plot(data$time.s, data$psi.t..rad, main = "angular frequency vs time", sub = alldata[i],
       xlab = "time (s)",
       ylab = "angular frequency (rad)",
       type = "p",
       xlim = c(0,15),
       ylim = c(-3,0))
    lines(data$time.s, data$psi.t..rad, col = "blue")
    dev.print(device = pdf, file = "Rplot5_20.pdf", width = 300)
    plot(data$time.s, data$psi.t..rad, main = "angular frequency vs time", sub = alldata[i],
       xlab = "time (s)",
       ylab = "angular frequency (rad)",
       type = "p",
       xlim = c(60,70))
       #ylim = c(-3,0)),
    lines (data$time.s, data$psi.t..rad, col = "green")
  }

  #omega <- NULL

  #delta_teta <- as.data.frame(data$psi.Max - data$psi.Min)
  
  #diff_teta[1] <- data$psi.Min[1]
  #diff_teta <- as.data.frame(c(diff_teta, diff(data$psi.Min)))

  #colnames(delta_teta)[1] <- "delta_teta"
  #colnames(deffi_teta)[1] <- "omega"
  #delta_teta <- na.omit(delta_teta)
  #diff_teta <- na.omit(diff_teta)
  
  #setwd(path_output)
  #write.table(delta_teta, file = paste0("delta_teta_", alldata[i]), row.names = FALSE)
  #write.table(diff_teta, file = paste0("delta_teta_", alldata[i]), row.names = FALSE)
   
  #viscosity <- as.vector(omega[,1])
  #elasticity <- as.vector(diff_teta[,1])

  #Maximum
  file = paste("film", str_extract(alldata[i], "\\d+")[1], sep ="_")
  #Maximum_curve(file)
  #Maximum_chg(file)
  #Maximum_drop(file)
  #Maximum_period(file)
  #Maximum_point(file)
  
  break
}
```


```{r}
plot(data$time.s[1:1800], diff(data$psi.t..rad), type = "l", ylim = c(-0.1, 0.2), xlim = c(0, 50)) #detrending

#plot(diff(data$psi.t..rad), type = "l", ylim = c(-0.1, 0.2))

#plot(diff_max)
#lines(diff_max)


nb <- nrow(data)/nrow(max)
nb

vec <- NULL
start <- 1
for (i in start:nrow(data)) {
  vec[i] <- data$psi.t..rad[i]
  if (i >= nb) {
    start <- i
    nb <- nb*2
  }
}

chg <- NULL # changements relatifs
for (i in 1:nrow(data)) {
  if (i == nrow(data)) { break }
  chg[i] <- (data$psi.t..rad[i+1]-data$psi.t..rad[i])/data$psi.t..rad[i]
}
plot(chg, ylim = c(-0.1, 0.1), xlim = c(1500, 1550))
lines(chg)
abline(h = 0, col = "blue") # on prends i-2
#si dessus alors courbe monte
#which(chg == 0)
```

